Correlating Scanning Ion Conductance and Super-Resolved Fluorescence Microscopy

### 2020-10-03 sections/correlated-sicm-and-fm.tex

\section{Correlating SICM and Fluorescence Microscopy}
\label{sec:correlating-sicm-and-fm}
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../manuscript"
%%% End:
Correlative SICM and FM, despite the mismatch in resolution, allows to gather
information which cannot be obtained by using a single technique
alone. However, the degree of correlation differs, depending on the FM
technique combined with SICM. Combining SICM and wide-field FM allows to image
the same region of the sample, which, for example, can be used to find a
region of interest such as an area containg synapses in a culture of a
neuronal network \cite{Novak2013,Scheenen2015}.

@@

>>>>

\section{Correlating SICM and Fluorescence Microscopy}
\label{sec:correlating-sicm-and-fm}
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../manuscript"
%%% End:

Correlative SICM and FM, despite the mismatch in resolution, allows to gather
information which cannot be obtained by using a single technique
alone. However, the degree of correlation differs, depending on the FM
technique combined with SICM. Combining SICM and wide-field FM allows to image
the same region of the sample, which, for example, can be used to find a
region of interest such as an area containg synapses in a culture of a
neuronal network \cite{Novak2013,Scheenen2015}.

@@

Correlative SICM and fluorescence microscopy opens up the opportunity to receive information, 
which are hidden and impossible to obtain by using one of this microscopy techniques alone. 
This is especially helpful for applications, where the reaction is not limited to \emph{one 
dimension}, for example when investigating the uptake of nanoparticles into cells. There it would 
be interesting to investigate both the cell membrane with a technique, which is able to do so -- 
AFM \cite{Binnig1986}, EM \cite{}, SICM \cite{Hansma1989} -- and the uptake of nanoparticles into 
cells or how the cytoskeleton react on the addition of the nanoparticle by using fluorescence 
microscopy methods.

% Den Teil brauchen wir ja vielleicht nicht. 
AFM, a method belonging to the scanning probe microscopy techniques, was successfully
combined to fluorescence microscopy techniques e.g. to investigate the topography of a 
cell or a part of a cell with the cytoskeleton \cite{Laishram2009,Liu2020}. But a big problem 
with this method is, that it is not the most favorable for investigating living cells in their
physiological surrounding. Certain destructive effects on the cell were found by using this 
technique \cite{You2000,Rheinlaender2011}. A better fitting method for investigating living cells 
would be scanning ion conductance microscopy (SICM) \cite{Hansma1989}.
